---
title: "Simulating Data"
format: html
editor: visual
---

## Introduction

This is an initial analysis where I 
generate a dataset that is meant to somewhat 
simulate the UK Labour Force Survey (LFS) dataset.

I'm doing this because I'm interested in learning 
more about sampling, weighting, and estimation. This
is just my understanding, I may get things wrong here.

Information on sampling can be found [here](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/employmentandemployeetypes/methodologies/labourforcesurveylfsqmi). 

### Sampling

It seems that sampling is done using the Postcode Address
File (PAF). A big file with all the postcodes, and all the 
addresses associated with these postcodes. This is the case 
except for north of the Caledonian canal which has another 
sampling frame as it's much less densely populated.
frame, but I'm going to ignore that for now.

Some postcodes have more/less houses. Some households 
have more or less people. 

The weight




```{r}
#| message: false
#| warning: false
#| error: false
# Packages for Reading and Tidying Data
library(readr)
library(tidyr)
library(dplyr)
#----------
library(ggplot2) # Plotting library 
library(dagitty) # For DAGs

library(brms) # For Bayesian modelling
library(ReGenesees) # For weighting and estimation
```


```{r}

set.seed(123)

generate_postcodes <- function(){

}

generate_households <- function(){
  
}

generate_individuals <- function(){
  
}




```

